\LARGE \bf Autonomous Object Manipulation using a Soft Planar Grasping Manipulator

### 2015-10-12 robotic_gripper.tex
two comments left for reviewer 1

\section{Soft Grasping Manipulator}
\label{sec:soft_grasping_manipulator}
\rkk{The robotic manipulator is composed of multiple bidirectional planar arm segments and combined with a unidirectional soft gripper.}
%We first introduce the previously developed uniform channel design, which is used for the soft body arm segments.
%Following this, 
We describe briefly the design, fabrication and functionality of this soft grasping manipulator. Further details on the design and fabrication can be found in \cite{marchese2015recipe}.

@@

\begin{figure}[thpb]
\centering
   \includegraphics[width=0.90\columnwidth]{figures/robotic_gripper/design_gripper.eps}
   \caption{The pleated channel designs. (\textbf{A}) depicts the segment in an unactuated state and (\textbf{B}) shows the segment in an actuated and therefore bent state. The expansion of the pressurized channels are schematically represented.}
   \label{fig:design}
\end{figure}

@@

\begin{figure}[htb]
\centering
   \includegraphics[width=0.98\columnwidth]{figures/robotic_gripper/fabrication_new.eps} %fab_pleated_process_horizontal_no_labels.eps
      \caption{Gripper fabrication process. (\textbf{A}) Pour and cure a rubber mold \rkk{(blue)}, (\textbf{B}) pour wax core \rkk{(yellow)} with embedded supportive rod \rkk{(brown)}, (\textbf{C}) combine bottom mold \rkk{(green)}, top mold \rkk{(grey)} and wax core using pins, (\textbf{D}) pour \rkk{softer} rubber \rkk{(light green)} into assembled mold, (\textbf{E}) pour stiffer rubber \rkk{(blue)} on top of the cured gripper \rkk{(light green)} to form a constraint layer, (\textbf{F}) remove cured gripper from mold, (\textbf{G}) using an oven melt out wax core from the gripper, and (\textbf{H}) add silicone tubing and plug using silicone sealant. \rkk{Reproduced from \cite{marchese2015recipe}.}}
      \label{fig:fabrication}
\end{figure}

>>>>

\section{Soft Grasping Manipulator}
\label{sec:soft_grasping_manipulator}
\rkk{The robotic manipulator is composed of multiple bidirectional planar arm segments and combined with a unidirectional soft gripper.}
%We first introduce the previously developed uniform channel design, which is used for the soft body arm segments.
%Following this, 
We describe the design, fabrication and functionality of this soft grasping manipulator. Further details on the underlying design and fabrication recipes can be found in \cite{marchese2015recipe}.

@@

\begin{figure}[thpb]
\centering
   \includegraphics[width=0.90\columnwidth]{figures/robotic_gripper/design_gripper.eps}
   \caption{The pleated channel designs. (\textbf{A}) depicts the segment in an unactuated state and (\textbf{B}) shows the segment in an actuated and therefore bent state. The expansion of the pressurized channels are schematically represented. \rkk{Reproduced from \cite{marchese2015recipe}.}}
   \label{fig:design}
\end{figure}

\begin{figure}[!ht]
\centering
   \includegraphics[width=0.85\columnwidth]{figures/robotic_gripper/fabrication_upright.eps} %fab_pleated_process_horizontal_no_labels.eps
      \caption{Gripper fabrication process. (\textbf{A}) Pour and cure a rubber mold \rkk{(blue)}, (\textbf{B}) pour wax core \rkk{(yellow)} with embedded supportive rod \rkk{(brown)}, (\textbf{C}) combine bottom mold \rkk{(green)}, top mold \rkk{(grey)} and wax core using pins, (\textbf{D}) pour \rkk{softer} rubber \rkk{(light green)} into assembled mold, (\textbf{E}) pour stiffer rubber \rkk{(blue)} on top of the cured gripper \rkk{(light green)} to form a constraint layer, (\textbf{F}) remove cured gripper from mold, (\textbf{G}) using an oven melt out wax core from the gripper, and (\textbf{H}) add silicone tubing and plug using silicone sealant. \rkk{Reproduced from \cite{marchese2015recipe}.}}
      \label{fig:fabrication}
\end{figure}

@@

### 2015-10-12 system_overview.tex
two comments left for reviewer 1

\section{System Overview}
\label{sec:System_Overview}
The aggregate system is shown in Figure \ref{fig:sys_overview} and consists of a manipulator, a gripper, an object, a tracking system, control computers, a fluidic drive array and a rigid frame.
The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
A soft rubber gripper is fixed to the tip of the manipulator.
An object is randomly placed within the reachable envelop of the manipulator. 
A motion capture system provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
The grasp motion planning algorithm as well as the curvature controller run on the control computers and take the tracking information as input.
The curvature controller then provides continuous closed-loop adjustment of the fluidic drive cylinder array.
The cylinder array directly actuates the manipulator and gripper.
A rigid frame holds all the subsystems together providing reliable and consistent hardware experiments.

\begin{figure}[htbp]
\begin{centering}
  \includegraphics[width=2.0in]{Figures/system_overview/sys_overview_smaller}\\
  \caption{System Overview. The system is composed of a motion capture system (A), rigid frame (B), soft six segment planar manipulator (C), an object within the grasp envelope (D), a soft gripper fixed to the manipulator (E), a fluidic drive cylinder array to control actuation (F), and computers for real-time processing and control (G).} \label{fig:sys_overview}
\end{centering}
\end{figure}

>>>>

\section{System Overview}
\label{sec:System_Overview}
The aggregate system is shown in Figure \ref{fig:sys_overview} and consists of a manipulator, a gripper, an object, a tracking system, control computers, a fluidic drive array and a rigid frame.
The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
A soft rubber gripper is fixed to the tip of the manipulator.
An object is randomly placed within the reachable envelop of the manipulator. 
A motion capture system provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
\rkk{We used the motion capture system OptiTrack Flex 3 by by Natural Point, Inc.}
The grasp motion planning algorithm as well as the curvature controller run on the control computers and take the tracking information as input.
The curvature controller then provides continuous closed-loop adjustment of the fluidic drive cylinder array.
The cylinder array directly actuates the manipulator and gripper.
A rigid frame holds all the subsystems together providing reliable and consistent hardware experiments. 
\rkk{The frame serves also as a mobile presentation platform that keeps the complete system together and holds the tracking cameras rigidly in place, not requiring recalibration after moving the system around.}

\begin{figure}[htbp]
\begin{centering}
  \includegraphics[width=2.0in]{Figures/system_overview/sys_overview_smaller}\\
  \caption{System Overview. The system is composed of (\textbf{A}) a motion capture system, (\textbf{B}) rigid frame, (\textbf{C}) soft six segment planar manipulator, (\textbf{D}) an object within the grasp envelope, (\textbf{E}) a soft gripper fixed to the manipulator, (\textbf{F}) a fluidic drive cylinder array to control actuation, and (\textbf{F}) computers for real-time processing and control.} \label{fig:sys_overview}
\end{centering}
\end{figure}
